---
title: "Module 2 - Notes and Exercises"
author: "<Your Name>"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: yes
    theme: journal
    highlight: haddock
    code_folding: hide
    fig_caption: yes
---


```{r, code = readLines("setup.R"), cache = FALSE, include=FALSE}
```

```{r}
knitr::opts_chunk$set(cache = TRUE, autodep = TRUE)
```




# Multi-armed bandits {#mod-bandit}

This module gives a short introduction to Reinforcement learning. 

## Learning outcomes 

By the end of this module, you are expected to:

<!-- * Describe what VBA is. -->
<!-- * Setup Excel for VBA. -->
<!-- * Know how the macro recorder works. -->
<!-- * Make your first program. -->
<!-- * Have an overview over what VBA can do. -->
<!-- * Recorded you first macro using the macro recorder -->

<!-- The learning outcomes relate to the [overall learning goals](#mod-lg-course) number 2 and 4 of the course. -->

<!-- SOLO increasing: identify · memorise · name · do simple procedure · collect data · -->
<!-- enumerate · describe · interpret · formulate · list · paraphrase · combine · do -->
<!-- algorithms · compare · contrast · explain causes · analyse · relate · derive · -->
<!-- evaluate · apply · argue · theorise · generalise · hypothesise · solve · reflect -->


## Textbook readings

For this week, you will need to read Chapter 2 in @Sutton18. Read it before continuing this module.



## Exercises {#sec-bandit-ex}



### Exercise - Self-Play {#ex-r-intro-self}



Consider Tic-Tac-Toe and assume that instead of an RL player against a random opponent, the reinforcement learning algorithm described above
played against itself. What do you think would happen in this case? Would it learn a different way of playing?






```{r links, child="links.md", include=FALSE}
```
